### 2016-07-07 motivation.tex
Edit.
Edits.

\caption{\small For the example in Fig.~\ref{fig:motiv-eg-1},
$\psi_{SI}$ specification allows $\hbZ$ arrows (hence the execution)
in Fig.~\ref{fig:hb-eg-1}. $\psi_{RC}$ specification allows
Figs.~\ref{fig:hb-eg-1},~\ref{fig:hb-eg-2},~\ref{fig:hb-eg-3}, and
~\ref{fig:hb-eg-4}. Each arrow represents an $\hbZ$ relationship
between all operations of \C{Wd2} and an operation in \C{Wd1}. Letters
R, W and C stand for read, write and commit, respectively.}
\label{fig:motiv-eg-1-hb}
\vspace*{-8pt}
\end{figure}

>>>>

\caption{\small Possible executions for the example in
Fig.~\ref{fig:motiv-eg-1}. Letters R, W and C stand for read, write
and commit, respectively. Each blue dashed arrow represents a $\hbZ$
relationship between all operations of \C{Wd2} and an operation in
\C{Wd1}. $\psi_{SI}$ specification allows $\hbZ$ arrows (hence the
execution) in Fig.~\ref{fig:hb-eg-1}. $\psi_{RC}$ specification allows
$\hbZ$ arrows in
Figs.~\ref{fig:hb-eg-1},~\ref{fig:hb-eg-2},~\ref{fig:hb-eg-3}, and
~\ref{fig:hb-eg-4}.  }
\label{fig:motiv-eg-1-hb}
\vspace*{-8pt}
\end{figure}
